---
title: "Coursera Course Project Part 2"
author: "Patrick"
date: "12/28/2016"
output: html_document
---

## Part 2 Tooth Growth Data

For the second part of the course project we are to compare the tooth growth data
for two groups; groups that took 'OJ' supp, and another group that took 'VC' supp.
these comparisons will be made at three seperate levels, depending on the dosage
taken by the participants (.5, 1 or 2)


# Data summary regarding dosage

First we will explor the data by comparing the two seperate groups with regards to dosage
```{r}
library(datasets) 
library(ggplot2) 

g <- ggplot(ToothGrowth, aes(factor(dose), len )) +
                        geom_boxplot() + facet_grid(.~supp)
print(g)

```
there apprears to be a upwards trend in both groups as dosage increases. 'Supp' also
seems to affect the groups differently for the first two dosages.

# Subsetting data
next we will subset our dataframe by dosage amount so we can run t-tests and compare the different groups.
```{r}

data(ToothGrowth) 
doseGrowth1 <- subset(ToothGrowth, dose == 0.5) 
doseGrowth2 <- subset(ToothGrowth, dose == 1)
doseGrowth3 <- subset(ToothGrowth, dose == 2)

```

now that we have subset our toothGrowth dataset with regards to dose, we will 
now conduct three tests to determine if there is a difference between 'OJ'
and 'VC" supp groups:

test1
h0: dosegrowth1(VC) = dosegrowth1(OJ)
test2
h0: dosegrowth2(VC) = dosegrowth2(OJ)
test3
h0: dosegrowth3(VC) = dosegrowth3(OJ)

# Test1
```{r}
t.test(len~supp, data = doseGrowth1)
```
The results of this t-test seem to indicate for a dose of .5 there is a 
significant difference between the two supp groups (p<.05).

# Test2
```{r}
t.test(len~supp, data = doseGrowth2)
```
The results of this t-test seem to indicate for a dose of 1 there is a 
significant difference between the two supp groups (p<.05).

# Test3
```{r}
t.test(len~supp, data = doseGrowth3)
```
for the last dosage group there does not seem to be a difference between
the two groups (p>.05) therefore the null hypothesis is not rejected.
