---
title: "Coursera Course Project Part 1"
author: "Patrick"
date: "12/28/2016"
output: html_document
---

## Part 1
```{r}

## set parameters
numsim <- 1000
n <- 40
lambda <- .20
set.seed(123)

simulation1 <- matrix(rexp(numsim*n, rate = lambda), numsim)
simulationmeans <- apply(simulation1, 1, mean)

hist(simulationmeans)

```

# 1.1 Theoretical distribution vs sample distribution
no we compare the distributions of the sample mean versus the theoretical mean
```{r}

actual_mean <- mean(simulationmeans)
theoretical_mean <- 1/lambda
print(actual_mean)
print(theoretical_mean)

```
the sample mean (5.01) approximates the theoretical mean (5.0), not quite the same but almost.


# 1.2 Theoretical Variance vs Sample Variance
```{r}

sample_variance <- var(simulationmeans)
theoretical_variance <- (1/lambda)^2/n
print(sample_variance)
print(theoretical_variance)

```
Again the sample mean (.608) approximates the theoretical variance ( .625)

# 1.3 demonstrate distribution approximates normal distribution
```{r}
hist(simulationmeans)
```
from the looks of the graph our data does indeed seem to be normaly distributed.

We can run a run a Shapiro-Wilk test to support our observation.
```{r}
shapiro.test(simulationmeans)
```

